Report

### 2021-05-03 Rmd/report.Rmd
Add longitudinal language profile plot

---
title: "Report"
output:
  html_document:
    df_print: paged
---

@@

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

@@

### vocabualry in the dominant language (L1)

@@

### Aggregated by trial

@@

## By age group

@@

## Effect of vocabulary

### Aggregated by time bin

@@

```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		)
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time_vocab.png"))

@@

@@

>>>>

---
title: "Report"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
---

@@

## Sample sizes

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid")) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

## Language profiles

Only valid participants.

```{r lps, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	filter(valid_participant) %>% 
	ggplot(aes(age, doe_2, colour = lp)) +
	facet_grid(test_language~location) +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 3, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 20, xmax = 22, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 24, xmax = 26, ymin = -Inf, ymax = Inf) +
	annotate(geom = "rect", alpha = 0.25, fill = "grey", colour = NA,
			 xmin = 28, xmax = 32, ymin = -Inf, ymax = Inf) +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(labels = percent) +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(linetype = "dotted", colour = "grey"),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		axis.text.y = element_text(size = 10)
	) +
	ggsave(here("Figures", "lps.png"))
```

@@

### Vocabulary in the dominant language (L1)

@@

### Target fixations: Age group and language profile {.tabset .tabset-pills}

#### Cross-sectional

@@

#### Longitudinal

Each trial was divided into 100 ms time bins. for each time bin, the proportion of  target fixations were calculated, from the total of fixations to the target, distractor and the rest of the screen for that same time bin. Proportions were then aggregated across trials for each time bin and participants, so that each participant contributed with 20 data points (one for each time bin) for each trial type (cognate, non-cognate, and unrelated). This figure shows the fitted line of a General Additive Model (GAM) generated using the `geom_smooth()` function from the `ggplot` R package, with default settings.

@@

### {-}

### Target fixations: Time course analysis

@@

### Target fixations: Vocabulary size

### Target fixations: High vocabulary vs. low vocabulary {.tabset .tabset-pills}

```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months")
	) %>% 
	drop_na()

@@

#### Age group: 21 months

```{r gaze_time_vocab_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

#### Age group: 25 months

```{r gaze_time_vocab_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "25 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

#### Age group: 30 months

```{r gaze_time_vocab_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "30 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

```
### {-}

@@

# References
